State of the Practice for Medical Imaging Software Based on Open Source Repositories

### 2025-01-26 StateOfPractice/Papers/SOP_MI_CritReviewsBioMedEng/ResubmissionResponseToReviewer.tex

  Some of the reviewer's questions are best answered by citing our related work.
  Therefore, the new version undoes the redaction originally added for the
  double blind review.

  \textbf{Reviewer \#1}

  \begin{enumerate}
  \item The relative priorities of each software quality were set equal.
  Couldn't some different weighting have been considered? Perhaps one that comes
  from interviews with developers or cited in papers? \medskip

  \emph{The reviewer is correct that other weightings could be considered.  We
  left this out of the scope of the original submission because of space
  considerations and because determining a meaningful alternative weighting is
  difficult.  Although Nguyen-Hoan et al.\ (2010) (A Survey of Scientific
  Software Development) provides survey data on the relative importance of
  various software qualities, their list of qualities differs from ours.  We are
  not aware of a recent survey that assesses the relative importance of
  qualities for scientific software. Moreover, even if we have quality
  priorities for all scientific software, our paper focuses only on medical
  imaging software.  The priorities for medical imaging software likely differ
  from the priorities for other scientific applications.  Furthermore, the
  priorities likely differ between different medical imaging applications.
  Rather than speculate on the relative priorities, we used the simplest case of
  equal priority. For any readers that would like to apply their own priorities,
  we can direct them to the spreadsheet used to generate the results shown in the
  paper.  With some simple modifications the plots can regenerated with whatever
  priority ranking a user wishes to see.  To make this clear, we have added the
  following text to the revised paper:  } \smallskip

  \textcolor{blue}{(Alternative priority schemes can be investigated by changing
the Prioritization Matrix in
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/AHP2021/MedicalImaging/AHP_Template.xlsx}
{AHP\_Template.xlsx} available on GitHub.)}

@@

  \item In addition to github, could any other reference have been used, such as
  the number of citations in papers or relevant websites in the field? \medskip

  \emph{Although the idea of including citations in papers is a good one, we
  have excluded this data because we feel it is unreliable.  Unfortunately,
  software is infrequently and inconsistently cited even when it is used (as
  observed by Smith et al (2016) (Software Citation Principles)).  Similar
  inconsistency problems exist for data on websites.  For other readers who have
  the same observation as the reviewer, we have added the following text to the
  revised version: \smallskip}

  \textcolor{blue}{We considered also comparing software citations, but this
  measure of popularity would be unreliable since software is infrequently and
  inconsistently cited (SmithEtAl2016).}

@@

  \item Where are the quality ratings for each software? \medskip

  \emph{The quality ratings for each software are summarized in Figure 2
  (Overall AHP scores with an equal weighting for all 9 software qualities). To
  keep the length of the paper reasonable, we do not have figures showing the
  ranking of the software packages for each quality, but this information is
  available through the citations given in the now unredacted revised version of the
  paper.  Some of the relevant citations include Dong (2021) (Assessing the
  state of the practice for medical imaging software, MEng thesis), and Smith et
  al (2024) (State of the practice for medical imaging software, extended report
  on arXiv). \smallskip}

@@

  \item Caption tables above them, not below them. \medskip

  \emph{This has been fixed in the revised manuscript. \smallskip}

  \item What are the possible reasons for the differences between the ranking
  found and that of GitHub, in addition to the impossibility of installing some
  of them? \medskip

  \emph{Other possible reasons for the differences in ranking are covered in the
  original submitted paper in the following text: ``We weighted all qualities
  equally, which is not the likely the same weighting that users implicitly use.
  To properly assess this would require a broad user study.  Furthermore our
  measures of popularity (like stars) are only \emph{proxies} which are biased
  towards past rather than current preferences (Szulik2017), as these are
  monotonically increasing quantities. Finally there are often more factors than
  just quality that influence the popularity of products.''  Given that this
  wasn't obvious to the reviewer, we strengthened the topic sentence that
  introduced the reasons with the following text: \smallskip}

  \textcolor{blue}{Besides the installation problem, another possible reason for
  discrepancies between our ranking and GitHub popularity is that we weighted
  all qualities equally, ....}

@@

  \item Some software could not be installed. What problems were found? Why not
  remove it from the list? \medskip

  \emph{In the interest of space, we have chosen to not include the details in
  on installation problems for \textit{GATE}, \textit{dwv}, and \textit{DICOM
  Viewer} in the paper.  Instead, the additional details are given in the
  extended version of the paper on arXiv (Smith et al (2024)) and in the
  associated Masters thesis (Dong (2021)).  The software with installation
  problems was not removed from our review because we aimed for as complete an
  overview as possible.   Moreover, the installation problems only affected the
  score on installability, reliability and robustness.  The other qualities are
  based on the artifacts in the repository, not on running the software.  To
  clarify this for readers of the paper, we have added text to the methodology
  for grading in the revised manuscript: \smallskip}

  \textcolor{blue}{We explicitly note any software that cannot be installed,
  but for completeness we still measure it for the remaining qualities, since
  only reliability and robustness require running the software.}

@@

  \textbf{Reviewer \#2}

  \begin{enumerate}

  \item The introduction section should contain the scope, significance of the
  research by summarizing current understanding and background information,
  stating the purpose of the work, and highlighting the potential outcomes.
  Also, there's no need to divide various subsection in the introduction.
  \medskip

  \emph{We believe that our introduction covers the scope (in Section 1.2 of the
  submitted version) the significance (in the first paragraph).  We also believe
  that the current understanding, background information and potential outcomes
  are covered by the research questions. There is not a considerable amount of
  background information because there isn't a previous study (that we are aware
  of) that assesses the state of the practice for medical imaging software. The
  potential outcomes are the answers to the research questions. \smallskip}

  \emph{The criticism of the introduction, including the comment about not
  having subsections, is likely due to our covering the methodology in the
  introduction section. In the revised version, we have made the methodology its
  own section and removed the subsections from the introduction. \smallskip}

@@

  \item The title of the table should be placed above the table. \medskip

  \emph{This has been fixed in the revised manuscript.  \smallskip}

  \item It is not recommended to include tables in the conclusion. \medskip

  \emph{Although including a table in the conclusions is rare, we think it is
  appropriate for this paper.  A table is a quickest way to summarize the
  software package quality.  Summarizing the same information in words would be
  hard to follow.  A conclusion shouldn't introduce new information, but the
  table is not new information; it is an alternate view of the information
  presented in Section 4 of the paper.  This new view makes some conclusions
  about the state of the practice clear, so it feels appropriate for the
  conclusion section. \smallskip}

### 2025-01-26 StateOfPractice/Papers/SOP_MI_CritReviewsBioMedEng/SOP_MI_OSR.tex
Resubmission version with reviewers comments addressed.

\subsection{Research Questions} \label{sec_motivation}

@@

\subsection{Scope} \label{sec_scope}

@@

\subsection{Methodology} \label{SecMethodology}

@@

\subsubsection{Domain Expert} \label{sec_vet_software_list}

@@

\subsubsection{Software Qualities} \label{sec_software_quality}

@@

\subsubsection{Grading} \label{sec_grading_software}

We use an existing template \cite{SmithEtAl2021} %% DOUBLE BLIND
that is designed to measure the
aforementioned qualities. To stay within our given measurement time frame, each
package gets up to five hours of time.  Project developers can be contacted for
help regarding installation, if necessary, but we impose a cap of about two
hours on the installation process.  Figure~\ref{fg_grading_template_example}
shows an excerpt of the measurement spreadsheet.  The rows are the measures and
the columns correspond to the software packages.  Dong (2021)~\cite{Dong2021-Data}
provides the full set of measurement data.   %%DOUBLE BLIND

@@

\subsubsection{Analytic Hierarchy Process (AHP)} \label{sec_AHP}

@@

\subsubsection{Interview Methods} \label{sec_interview_methods}

@@

We measured the software as described in
Section~\ref{SecMethodology}.  In the absence of a specific real world context,
we assumed all nine qualities are equally important.
Figure~\ref{fg_overall_scores} shows the overall AHP scores in descending order.

@@

We use GitHub stars, number of forks and
number of people watching the projects as proxies for community ranking.
Table~\ref{tab_ranking_vs_GitHub} show the statistics for data collected in July
2021.

@@

We weighted all qualities equally, which is not the likely the same weighting
that users implicitly use. To properly assess this would require a broad user
study.  Furthermore our measures of popularity (like stars) are only \emph{proxies} which
are biased towards past rather than current preferences~\cite{Szulik2017}, as
these are monotonically increasing quantities. Finally there are often more
factors than just quality that influence the popularity of 
products.

@@

We interview data, as described in Section~\ref{sec_interview_methods}
to answer \rqref{RQ_CompareToolsProjMngmnt} (tool usage),
\rqref{RQ_CompareMethodologies} (methodology) and \rqref{RQ_PainPoints} (pain
points). Requests were sent to all 29 projects.  Nine developers from eight of
the projects agreed to participate: \textit{3D Slicer}, \textit{INVESALIUS 3},
\textit{dwv}, \textit{BioImage Suite Web}, \textit{ITK-SNAP},
\textit{MRIcroGL}, \textit{Weasis}, and \textit{OHIF}. We spent about 90
minutes for each interview. The full interview answers can be
found in [citation redacted for blind review].
%\cite{Dong2021}.

@@

\paragraph{CI/CD} 
Only 17\% of MI projects use CI/CD tools. We estimated this using artifacts
present in the repository -- actual usage may be higher as some tools are
entirely external. This was the case for a study of Lattice Boltzmann Method
(LBM) software [citation redacted for blind review].  %\cite{Michalski2021}.
This contrasts with the high frequency of guidelines recommending continuous
integration
\cite{BrettEtAl2021, Brown2015, ThielEtAl2020, Zadka2018, vanGompelEtAl2016}.
A recent survey~\cite{CarverEtAl2022} of practitioners (rather than projects)
suggests higher use of CI/CD with 54\% of respondents indicating that they use
it.

\paragraph{Documentation} The most popular (mentioned by about 30\% of
developers) were forum discussions and videos.  The second most popular options
(20\%) were GitHub, wiki pages, workshops, and social media. The least
frequently mentioned options (about 10\% of developers) included writing books,
and Google forms.  As a point of contrast, LBM software most often uses API
document generation tools, like doxygen and sphinx [citation redacted for blind
review].
%\cite{Michalski2021}

@@

This matches previous observations for other research software.  Scientific
software developers often use an agile philosophy \cite{AckroydEtAl2008,
CarverEtAl2007, EasterbrookAndJohns2009, Segal2005, HeatonAndCarver2015}, or an
amethododical process \cite{Kelly2013}, or a knowledge acquisition driven
process~\cite{Kelly2015}.  A waterfall-like process can work for research
software~\cite{Smith2016}, especially if the developers work iteratively and
incrementally, but externally document their work as if they followed a rational
design process~\cite{parnas1986rational}.

No interviewee mentioned a strictly defined project management process. The most
common approach was issue-driven via bug reports and feature requests.
[Redacted for blind review] %Dong~\cite{Dong2021} 
provides details on the specific approaches used by the interviewees.
% JC: I don't think this level of per-project detail makes sense in this
% review article - it should be about stats and trends, not reporting on
% minute details. We could refer the reader to Ao's thesis for the details.
% 
% SS: I've revised the text to not include the details
% The
% most common approach was following the issues, such as bugs and feature
% requests. The \textit{3D Slicer} team had weekly meetings to discuss
% the goals for the project. The \textit{INVESALIUS 3} team relied on the
% GitHub process for their project management while the \textit{ITK-SNAP} 
% team had a fixed six-month release pace. Only the interviewee from 
% \textit{OHIF} 
% mentioned the team having a project manager. The \textit{3D Slicer} team and
% \textit{BioImage Suite Web} team do nightly builds and tests. The \textit{OHIF}
% developer believes that a better project management process can improve junior
% developer efficiency while also improving internal and external communication.

Less than half of the projects used unit testing, even
though the interviewees believed that testing (including usability tests) was
the top approach to improve correctness, usability, and reproducibility.  This
level of testing matches what was observed for LBM
software [citation redacted for blind review]
%\cite{Michalski2021} 
and is apparently greater than the level of
testing for ocean modelling software~\cite{JungEtAl2022}.

@@

Pinto et al.~\cite{PintoEtAl2018} list other pain points not mentioned by our
interviewees: scope bloat, aloneness, lack of user feedback, interruptions while
coding, and collaboration challenges. Two more are~\cite{WieseEtAl2019}:
reproducibility, and software scope determination.  [citation redacted for blind
review] %\cite{SmithEtAl2024} 
adds lack of software experience, documentation and technical debt.  Our small
sample size means that we cannot conclude that these are not also issues with MI
software.

@@

\item[P\refstepcounter{pnum}\thepnum \label{P_LackDevTime}:] \textbf{Lack of
Development Time:} This was felt to be the most significant obstacle, and
is not uncommon
\cite{SmithEtAl2024, WieseEtAl2019, PintoEtAl2018, PintoEtAl2016}.
%DOUBLE BLIND  [redacted for blind review]

\item[P\refstepcounter{pnum}\thepnum \label{P_LackFunding}:] \textbf{Lack of
Funding:} As research software is not yet seen as essential infrastructure,
there is an ongoing struggle to attract funding to build and, even harder, maintain
research software. This is a common complaint~\cite{GewaltigAndCannon2012, Goble2014, KaterbowAndFeulner2018, SmithEtAl2024}. %,  %DOUBLE BLIND
Software output is not always counted when judging the academic excellence of
academics, which forces researchers who write software to spend extra time on
publicity~\cite{WieseEtAl2019}. In some domains, like
biology~\cite{HowisonAndBullard2016}, software is infrequently cited even when
used pervasively. In other words, there is a lack of a formal reward system for
research software~\cite{PintoEtAl2018}.

@@

At least to some extent the problems for MI software users are due to holes in
their knowledge of software and computing technology, and sometimes also
lack of expertize in their domain to be able to adequately use the software
\cite{WieseEtAl2019}. 
%A similar pattern has been observed during interviews with
%LBM software developers [citation redacted for blind review].
%\cite{SmithEtAl2024}.

@@

\begin{itemize}
    \item Remove headaches caused by a separate integration phase
    \cite{Fowler2006}, \cite[p.\ 20]{HumbleAndFarley2010}.
    \item Detection and removal of bugs \cite{Fowler2006} via
    automated testing.  
    \item The base is constantly stable for everyone, always passing all tests.
    \item The code will be standardized and the documentation current, if the CI
    system uses generators and linters.
\end{itemize}

@@

The pervasive use of such tools to enforce documentation standards partially
explains the relatively high quality of software in the Comprehensive R Archive
Network (CRAN) [citation redacted for blind review].
%\cite{SmithEtAl2018_StatSoft}.

@@

Latent defects can found on average at a rate of 60--65\% by rigorous
inspection, with this rate reaching as high as 85\% \cite{Jones2008}. The
success rate of code inspection is generally higher than via testing, since testing
averages around 30--35\% for the efficiency of defect removal \cite{EbertAndJones2009,
Jones2008}. For research software, Kelly and Shepard \cite{KellyAndShepard2000}
show a task based inspection approach can be effective.

@@

The advice to modularize scientific software to handle complexity is common
\cite{WilsonEtAl2014, StewartEtAl2017, Storer2017}; however, specific guidelines
on the criteria to use for modularization is rare.  Parnas~\cite{Parnas1972a}
shows that not every decomposition supports change.  For instance, a design with
high coupling and low cohesion will make change challenging~\cite[p.\
48]{GhezziEtAl2003}. Since change is frequent in research software, the best
modularizations will support change. The pain of not previously designing for
change is currently being felt by ocean modelling community~\cite{JungEtAl2022}.

>>>>

%\subsection{Research Questions} \label{sec_motivation}

@@

%\subsection{Scope} \label{sec_scope}

@@

\section{Methodology} \label{SecMethodology}

@@

\subsection{Domain Expert} \label{sec_vet_software_list}

@@

\subsection{Software Qualities} \label{sec_software_quality}

@@

\subsection{Grading} \label{sec_grading_software}

We use an existing template \cite{SmithEtAl2021} %% DOUBLE BLIND
that is designed to measure the
aforementioned qualities. To stay within our given measurement time frame, each
package gets up to five hours of time.  Project developers can be contacted for
help regarding installation, if necessary, but we impose a cap of about two
hours on the installation process.  We explicitly note any software that cannot be installed, but for completeness we still measure it for the remaining qualities, since only reliability and robustness require running the software. Figure~\ref{fg_grading_template_example}
shows an excerpt of the measurement spreadsheet.  The rows are the measures and
the columns correspond to the software packages.  Dong (2021)~\cite{Dong2021-Data}
provides the full set of measurement data.   %%DOUBLE BLIND

@@

\subsection{Analytic Hierarchy Process (AHP)} \label{sec_AHP}

@@

\subsection{Interview Methods} \label{sec_interview_methods}

@@

We measured the software as described in Section~\ref{SecMethodology}.  In the
absence of a specific real world context, we assumed all nine qualities are
equally important.  (Alternative priority schemes can be investigated by changing the
Prioritization Matrix in
\href{https://github.com/smiths/AIMSS/blob/master/StateOfPractice/AHP2021/MedicalImaging/AHP_Template.xlsx}
{AHP\_Template.xlsx} available on GitHub.) Figure~\ref{fg_overall_scores} shows
the overall AHP scores in descending order.

@@

We use GitHub stars, number of forks and
number of people watching the projects as proxies for community ranking.  We considered also comparing software citations, but this measure of popularity would be unreliable since software is infrequently and inconsistently cited~\cite{SmithEtAl2016-softcite}.
Table~\ref{tab_ranking_vs_GitHub} show the statistics for GitHub data collected in July
2021.

@@

Besides the installation problem, another possible reason for discrepancies between our ranking and GitHub popularity is that we weighted all qualities equally, which is not the likely the same weighting
that users implicitly use. To properly assess this would require a broad user
study.  Furthermore our measures of popularity (like stars) are only \emph{proxies} which
are biased towards past rather than current preferences~\cite{Szulik2017}, as
these are monotonically increasing quantities. Finally there are often more
factors than just quality that influence the popularity of 
products.

@@

We interview developers, as described in Section~\ref{sec_interview_methods}, to answer \rqref{RQ_CompareToolsProjMngmnt} (tool usage),
\rqref{RQ_CompareMethodologies} (methodology) and \rqref{RQ_PainPoints} (pain
points). Requests were sent to all 29 projects.  Nine developers from eight of
the projects agreed to participate: \textit{3D Slicer}, \textit{INVESALIUS 3},
\textit{dwv}, \textit{BioImage Suite Web}, \textit{ITK-SNAP},
\textit{MRIcroGL}, \textit{Weasis}, and \textit{OHIF}. We spent about 90
minutes for each interview. The full interview answers can be
found in Dong (2021)~\cite{Dong2021}. %%DOUBLE BLIND

@@

\paragraph{CI/CD} 
Only 17\% of MI projects use CI/CD tools. We estimated this using artifacts
present in the repository -- actual usage may be higher as some tools are
entirely external. This was the case for a study of Lattice Boltzmann Method
(LBM) software~\cite{Michalski2021}. %%DOUBLE BLIND
This contrasts with the high frequency of guidelines recommending continuous
integration
\cite{BrettEtAl2021, ThielEtAl2020, vanGompelEtAl2016, Brown2015, Zadka2018}.
A recent survey~\cite{CarverEtAl2022} of practitioners (rather than projects)
suggests higher use of CI/CD with 54\% of respondents indicating that they use
it.

\paragraph{Documentation} The most popular (mentioned by about 30\% of
developers) were forum discussions and videos.  The second most popular options
(20\%) were GitHub, wiki pages, workshops, and social media. The least
frequently mentioned options (about 10\% of developers) included writing books,
and Google forms.  As a point of contrast, LBM software most often uses API
document generation tools, like doxygen and sphinx~\cite{Michalski2021}. %%DOUBLE BLIND

@@

This matches previous observations for other research software.  Scientific
software developers often use an agile philosophy \cite{HeatonAndCarver2015, CarverEtAl2007, AckroydEtAl2008, EasterbrookAndJohns2009, Segal2005}, or an
amethododical process \cite{Kelly2013}, or a knowledge acquisition driven
process~\cite{Kelly2015}.  A waterfall-like process can work for research
software~\cite{Smith2016}, especially if the developers work iteratively and
incrementally, but externally document their work as if they followed a rational
design process~\cite{parnas1986rational}.

No interviewee mentioned a strictly defined project management process. The most
common approach was issue-driven via bug reports and feature requests.
Dong (2021)~\cite{Dong2021} %%DOUBLE BLIND
provides details on the specific approaches used by the interviewees.
% JC: I don't think this level of per-project detail makes sense in this
% review article - it should be about stats and trends, not reporting on
% minute details. We could refer the reader to Ao's thesis for the details.
% 
% SS: I've revised the text to not include the details
% The
% most common approach was following the issues, such as bugs and feature
% requests. The \textit{3D Slicer} team had weekly meetings to discuss
% the goals for the project. The \textit{INVESALIUS 3} team relied on the
% GitHub process for their project management while the \textit{ITK-SNAP} 
% team had a fixed six-month release pace. Only the interviewee from 
% \textit{OHIF} 
% mentioned the team having a project manager. The \textit{3D Slicer} team and
% \textit{BioImage Suite Web} team do nightly builds and tests. The \textit{OHIF}
% developer believes that a better project management process can improve junior
% developer efficiency while also improving internal and external communication.

Less than half of the projects used unit testing, even
though the interviewees believed that testing (including usability tests) was
the top approach to improve correctness, usability, and reproducibility.  This
level of testing matches what was observed for LBM
software~\cite{Michalski2021} %%DOUBLE BLIND
and is apparently greater than the level of
testing for ocean modelling software~\cite{JungEtAl2022}.

@@

Pinto et al.~\cite{PintoEtAl2018} list other pain points not mentioned by our
interviewees: scope bloat, aloneness, lack of user feedback, interruptions while
coding, and collaboration challenges. Two more are~\cite{WieseEtAl2019}:
reproducibility, and software scope determination.  Smith et al.\ (2024)~\cite{SmithEtAl2024} 
adds lack of software experience, documentation and technical debt.  Our small
sample size means that we cannot conclude that these are not also issues with MI
software.

@@

\item[P\refstepcounter{pnum}\thepnum \label{P_LackDevTime}:] \textbf{Lack of
Development Time:} This was felt to be the most significant obstacle, and
is not uncommon
\cite{SmithEtAl2024, WieseEtAl2019, PintoEtAl2018, PintoEtAl2016}.
%DOUBLE BLIND

\item[P\refstepcounter{pnum}\thepnum \label{P_LackFunding}:] \textbf{Lack of
Funding:} As research software is not yet seen as essential infrastructure,
there is an ongoing struggle to attract funding to build and, even harder, maintain
research software. This is a common complaint~\cite{SmithEtAl2024, GewaltigAndCannon2012, Goble2014, KaterbowAndFeulner2018}. %,  %DOUBLE BLIND
Software output is not always counted when judging the academic excellence of
academics, which forces researchers who write software to spend extra time on
publicity~\cite{WieseEtAl2019}. In some domains, like
biology~\cite{HowisonAndBullard2016}, software is infrequently cited even when
used pervasively. In other words, there is a lack of a formal reward system for
research software~\cite{PintoEtAl2018}.

@@

At least to some extent the problems for MI software users are due to holes in
their knowledge of software and computing technology, and sometimes also
lack of expertize in their domain to be able to adequately use the software
\cite{WieseEtAl2019}. 
A similar pattern has been observed during interviews with
LBM software developers \cite{SmithEtAl2024}. %%DOUBLE BLIND

@@

\begin{itemize}
    \item Remove headaches caused by a separate integration phase
    \cite[p.\ 20]{HumbleAndFarley2010}, \cite{Fowler2006}.
    \item Detection and removal of bugs \cite{Fowler2006} via
    automated testing.  
    \item The base is constantly stable for everyone, always passing all tests.
    \item The code will be standardized and the documentation current, if the CI
    system uses generators and linters.
\end{itemize}

@@

The pervasive use of such tools to enforce documentation standards partially
explains the relatively high quality of software in the Comprehensive R Archive
Network (CRAN)~\cite{SmithEtAl2018_StatSoft}. %%DOUBLE BLIND

@@

Latent defects can found on average at a rate of 60--65\% by rigorous
inspection, with this rate reaching as high as 85\% \cite{Jones2008}. The
success rate of code inspection is generally higher than via testing, since testing
averages around 30--35\% for the efficiency of defect removal \cite{Jones2008, EbertAndJones2009}. For research software, Kelly and Shepard \cite{KellyAndShepard2000}
show a task based inspection approach can be effective.

@@

The advice to modularize scientific software to handle complexity is common
\cite{Storer2017, WilsonEtAl2014, StewartEtAl2017}; however, specific guidelines
on the criteria to use for modularization is rare.  Parnas~\cite{Parnas1972a}
shows that not every decomposition supports change.  For instance, a design with
high coupling and low cohesion will make change challenging~\cite[p.\
48]{GhezziEtAl2003}. Since change is frequent in research software, the best
modularizations will support change. The pain of not previously designing for
change is currently being felt by ocean modelling community~\cite{JungEtAl2022}.
